\documentclass[10pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amssymb} 

\renewcommand{\P}{\mathbb{P}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\Var}{\mathrm{Var}}

\title{MCMT Homework 10}
\author{Shun Zhang}
\date{}

\begin{document}
\maketitle

\section*{Exercise 10.1}

$\mu((1, 2, \cdots, k) \rightarrow (2, 3, \cdots, k, 1)) = \frac{1}{n}$.

$\mu(\cdot) = 0$, for other permutations.

\section*{Exercise 10.2}

Let $p = 1 / (3^2)^3$, and consider the cases when $n = 3$, $\tau = 3$.

\begin{enumerate}
\item 
When $X_3 = X_0$, we may swap a card with itself at each time, and swap three
different cards for $t = 1, 2, 3$. The probability is $3!p = 6p$. We can also swap
two cards back and forth for the first two steps, and swap the third card with
itself. The probability is ${3 \choose 2} 2^2p = 12p$. So $\P(X_3 = X_0, \tau = 3)
= 18p$.

When $X_3 = (2\ 1\ 3)X_0$, which we stop at swaping two cards on the top. We can
swap any card with itself in the first two rounds, but include 3 at least once,
and then swap 1 and 2 in the third step. The probability is $5 * 2p = 10p$.
We can also swap the third card with either of the top cards back and forth for
the first two steps, and then swap 1 and 2 in the third step. The probability is
$2 * 2^3p = 16p$. We can conclude that $\P(X_3 = (2\ 1\ 3)X_0, \tau = 3) \geq
26p$.

$\pi$ is a uniform distribution, but $\P(X_3 = X_0, \tau = 3) \neq \P(X_3 = (2\
1\ 3)X_0, \tau = 3)$. So this is not a strong stationary distribution.

\item 
$R_t$ must be distinct for $t = 1, 2, 3$. So $P(\tau = 3) = 3! * 3^3p = 162p$.

When $X_3 = X_0$, we may swap a card with itself at each time, and swap three
different cards for $t = 1, 2, 3$. The probability is $3!p = 6p$. We can also
swap two cards back and forth for two steps, and swap the third card with itself
in the other step. The probability is ${3 \choose 2} {3 \choose 2} 2p = 18p$. So $\P(X_3 = X_0,
\tau = 3)
= 24p$.

There are 6 possible outcomes for $\tau = 3$, but $\P(X_3 = X_0, \tau = 3) \neq
162p / 6$. So this is not a strong stationary distribution.

\end{enumerate}

\end{document}
